method

### 2022-02-15 06_Paper/ER-ED/method.Rmd
added text to SVs

>>>>

To investigate, whether individual SVs predict ER choice, a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
Furthermore, an ordinal logistic regression with dependent variable choice and independent variables SVs of each strategy will be computed.
